Rank Verification for Exponential Families

### 2016-04-22 verifying-winner.tex
Discussion and psychology experiment added

\subsection{Outline}
\Cref{sec:maj} gives a formal definition of the condition we are imposing, as well as common examples satisfying the condition. \Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, as well as a demonstration of the power of this test. This section also explains the validity of level $\alpha$ conditional on the best population not winning. \Cref{sec:confbound,sec:stepdown} prove Procedure 2 and 3 are valid. We will finally examine a published study with our methods in \Cref{sec:conclusion}.

@@

\section{Conclusion}
\label{sec:conclusion}

>>>>

\subsection{Outline}
\Cref{sec:maj} gives a formal definition of the condition we are imposing, as well as common examples satisfying the condition. \Cref{sec:winnerbest} proves that an unadjusted pairwise test comparing the winner to the runner-up is valid, as well as a demonstration of the power of this test. This section also explains the validity of level $\alpha$ conditional on the best population not winning. \Cref{sec:confbound,sec:stepdown} prove Procedure 2 and 3 are valid. We will finally examine a published study with our methods in \Cref{sec:disc}.

@@

\section{Discussion}
\label{sec:disc}

Our selective test procedure allows us to untangle multiple comparisons based on correlated observations easily, while avoiding the pitfalls of selective inference. To illustrate, we look at a past psychology study done by \citet{Uhls:2012gf}.

\begin{table}[htbp]
\begin{center}
\begin{tabular}{c c}
	\hline
	Value & Count \\
	\hline
	Achievement & $3$ \\
	Benevolence & $5$ \\
	Fame & $8$ \\
	Community feeling & $2$ \\
	Financial success & $1$ \\
	Self-acceptance & $0$ \\
	Image & $0$ \\
	Other & $1$ \\
	\hline
\end{tabular}
\end{center}
\caption{The number of study participants who chose each value as their top desired one. Since only one options can be chosen, these observations are inherently multinomial.}
\label{tbl:fame}
\end{table}

A sample of $20$ students from elementary and middle schools were asked to choose a top ``value'' from 7 different options: achievement, benevolence, fame, community feeling, financial success, self-acceptance, image and other. The results are tabulated in \Cref{tbl:fame}. The study postulates that fame is significantly the top value of choice. It proceeds to perform a binomial test for the null hypothesis that the participants chose among the $7$ options uniformly and concluded with a $p$-value of $0.006$ that fame is indeed the top desired value. The analysis failed to address the ``winner's curse'', as well as the intricate dependence among the observations. Our paper addressed these two issues and provided a simple test --- perform a unadjusted (two-tailed) binomial test of the winner and the runner-up. In this case, we test if $8$ is a significant observation in $\text{Binomial}\left(8 + 5, 0.5\right)$. The two-tailed $p$-value is $0.580811$, suggesting that the study was inconclusive.
